\thetitle

### 2024-11-18 paper/paper.tex
Start the rewrite

\def \thetitle {Correcting supernova luminosity for redshift implies no accelerated expansion}
\title{\thetitle}

@@

\begin{abstract}
  Existing analysis of Type Ia supernova relies on the assumption that
  luminosity is not affected by redshift. However, when luminosity is corrected
  for redshift, the relationship between luminosity distance and redshift for
  Type Ia supernova becomes linear. This implies that the expansion rate of the
  universe is not accelerating and there is no need for dark energy to explain
  observational data.
\end{abstract}

@@

\section{Derivation of luminosity distance}

Luminosity distance $D_L$, is the apparent distance of an object based on the
observed luminisity, also known as the flux $F$.  This does not take into
account any movement of the observed object between the time when the light was
emitted and the light is observed. $D_L$ also does not take into account
redshift. We are instead interested in $D_{L^*}$, which is the distance based
on the luminosity corrected for redshift.

Measurements of Type Ia supernova provide magnitude and redshift. To derive the
luminosity distance from these measurements, we start by computing the flux
$L$. Magnitude $M$ is defined on a logarithmic scale where magnitude 1 has 100
times the brightness of magnitude 6, leading to

@@

This is proportional to the amount of energy detected by a telescope. However,
we instead want a number that is proportional to the number of photons detected
by the telescope. Redshifting decreases the amount of energy carried by a
photon from $E_{\text{emit}}$ to $E_{\text{obs}}$, but we can correct for this
phenomenon by taking

\begin{equation}
  F^{*} = F \frac{E_{\text{emit}}}{E_{\text{obs}}}.
\end{equation}

Since the energy for a photon is given by $E = \frac{hc}{\lambda}$ where $h$ is
the Planck constant and $c$ is the speed of light, we have

\begin{equation}
\begin{aligned}
  F^{*} &= F \frac{\frac{hc}{\lambda_{\text{emit}}}}{\frac{hc}{\lambda_{\text{obs}}}} \\
        &= F \frac{\lambda_{\text{obs}}}{\lambda_{\text{emit}}}.
\end{aligned}
\end{equation}

We use the redshift equation $(1 + z)\lambda_{\text{emit}} =
\lambda_{\text{obs}}$ to obtain

\begin{equation}
\begin{aligned}
  F^{*} &= B \frac{(1 + z)\lambda_{\text{emit}}}{\lambda_{\text{emit}}} \\
        &= B(1 + z).
\end{aligned}
\end{equation}

@@

We note that since all Type Ia supernova have approximately the same intrinsic
brightness, we can use a geometric model to compute relative distances. Imagine
holding up two coins, one in each hand.  If you arange them so that the
distance from your eyes to the first coin double the distance from your eyes to
the second coin, the second coin should appear to be $\frac{1}{4}$ of the size.
More formally, for two objects of the same radius $r$, the apparent area $A$
is

\begin{equation}
  A = \pi \bigg(\frac{r}{d}\bigg)^2
\end{equation}

where $D$ is the relative distance between the two objects.

Replacing the area with the brightness, we have

\begin{equation*}
  F^{*} = \pi \bigg(\frac{r}{D}\bigg)^2
\end{equation*}

\begin{equation}
\label{eq:D*}
  D_{L^*} = r \sqrt{\frac{\pi}{F^*}}.
\end{equation}

Since this equation has no specified units, we will need to find a
calibration factor $k$. To beautify the equation, we can collect all constants
(which includes $r$ since all Type Ia supernova have the same intrinsic
brightness) into $k$. This gives

\begin{equation}
\begin{aligned}
  D_{L^*} &= r \sqrt{\frac{\pi}{\frac{1}{\sqrt[5]{100}^{M - 1}}(1 + z)}} \\
          &= \frac{k 10^\frac{M}{5}}{\sqrt{z + 1}}.
\end{aligned}
\end{equation}

The results of this model are shown in Figure \ref{fig:corrected_uncalibrated}.

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/corrected_uncalibrated.png}
  \caption{Uncalibrated distance model using the corrected $F^*$ values for
  brightness. The data were obtained from \citet{betoule2014}.}
  \label{fig:corrected_uncalibrated}
\end{figure}

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/uncorrected_uncalibrated.png}
  \caption{Uncalibrated distance model using the uncorrected $F$ values for brightness.
  The deviation from linearity suggests that distant objects are
  farther away than expected due to an accelerated expansion rate.}
  \label{fig:uncorrected_uncalibrated}
\end{figure}

@@

To compute a model, we use non-parametric regression via repeated means as described in
\citet{siegel1982}. A comparison of both models is shown in Figure \ref{fig:calibrated}.

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/both_calibrated_velocity_vs_distance.png}
  \caption{Calibrated distance model using both the corrected $F^*$ values as
  well as the uncorrected $F$ brightness values.}
  \label{fig:calibrated}
\end{figure}

@@

\begin{displayquote}
  Specifically, the distance estimator used in this analysis (and in most
  similar cosmological analyses) assumes that supernovae with identical color,
  shape and galactic environment have on average the same intrinsic luminosity
  for all redshifts. This hypothesis is quantified by a linear model, yielding
  a standardized distance modulus $\mu = 5 \log_{10}{(d_L / 10 \text{pc})}$:

  \begin{equation}
  \label{eq:betoule_distance_modulus}
    \mu = m_B^* - (M_B - \alpha \times X_1 + \beta \times C)
  \end{equation}

  where $m_B^*$ corresponds to the observed peak magnitude in restframe $B$
  band and $\alpha$, $\beta$ and $M_B$ are nuisance parameters in the distance
  estimate.
\end{displayquote}

This statement may refer to the idea that a Type Ia supernova can have an
evolving intrinsic luminosity $L$ over time as conditions within the universe
change which was first hypothesized by \citet{tinsley1968}. In Equation
\ref{eq:betoule_distance_modulus}, there is no correction for redshift, which
suggests the interpretation that the flux $F$ is unaffected by redshift.

The model where $F$ is not corrected for redshift is explored in Figure
\ref{fig_uncorrected_uncalibrated} by replacing $F^*$ with $F$ in Equation
\ref{eq:D*} and obtaining

>>>>

\def \thetitle {Correcting supernova luminosity for time dilation implies no dark energy}
\title{\thetitle}

@@

\begin{abstract}
  Existing analysis of Type Ia supernova relies on the assumption that
  luminosity is not affected by time dilation. However, when luminosity is
  corrected for time dilation, the relationship between luminosity distance and
  redshift for Type Ia supernova becomes linear. This indicates that the
  expansion rate of the universe is not accelerating and there is no need for
  dark energy to explain observational data.
\end{abstract}

@@

\section{The dimming effects of redshift}

The characteristics of redshift depend on the reason distant objects are
redshifted. The dominant model is the big bang theory, where the farther away
an object is from us, the more quickly it is moving away from us. Another
theory is the tired light hypothesis, as described by \citet{shao2013}, where
distant objects are mostly stationary relative to us, but where the energy of
light is lost as it travels through space. A feature of the tired light
hypothesis is that since distant objects do not have a high relative velocity
to us, they should not show time dilation. However, as shown by
\citet{white2024}, distant supernova do experience time dilation. Based on
this, we reject the tired light hypothesis and assume the big bang model.

The magnitude measurements for Type Ia supernova goes through a long chain of
data processing. The data used here was collected by the Dark Energy Survey
Collaboration, as summarized in \citet{abbott2024}, while \citet{vincenzi2024}
describes the data processing pipeline in more detail. However, the data
processing does not explicitly correct for either redshift or time dilation.

In the big bang model, there are two phenomena associated with redshift that we
might expect to reduce the appearant magnitude of a Type Ia supernova. The
first phenomenon is that the energy carried by a photon is inversely
proportional to wavelength, so as redshift increases the wavelength of a
photon, the energy decreases. The second phenomenon is that time dilation for
objects moving quickly relative to our observational rest frame will reduce the
rate at which photons are being emitted.

The supernova data collected by the DES Collaboration used a CCD camera, a
photon counting device, as described by \citet{flaughter2015}.  As noted by
\citet{kim1996}, photometric measurements that depend on bolometers will need
to be corrected for the reduced energy level of redshifted light, but with a
photon counting device, this correction is not necessary.

However, time dilation also reduces the magnitude of light. Instead of changing
the properties of individual photons, it reduces the count of photons by a
factor of $\frac{1}{1+z}$. This phenomenon will not be addressed by the nuances
of any measuring device, so it must be explicitly corrected.

\section{Correcting magnitude for time dilation}

Luminosity distance $D_L$, is the apparent distance of an object based on the
observed luminosity, also known as the flux $F$. This does not take into
account any movement of the observed object between the time when the light was
emitted and the light is observed.

To derive the luminosity distance from these measurements, we start
by computing the flux $L$. Magnitude $M$ is defined on a logarithmic scale
where magnitude 1 has 100 times the brightness of magnitude 6, leading to

@@

This is proportional to the number of photons detected by a telescope. We can
find the corrected flux $F^*$ by multiplying by $k(z)$, the redshift correction factor. Time
dilation of quickly moving objects reduces the number of photons by a factor of
$\frac{1}{1 + z}$, so we have

\begin{equation}
\begin{aligned}
  F^* &= F \times k(z) \\
      &= F (1 + z).
\end{aligned}
\end{equation}

@@

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/mu_distance_vs_redshift.png}
  \caption{todo}
  \label{fig:corrected_uncalibrated}
\end{figure}

\begin{figure}[h!]
  \includegraphics[width=\linewidth]{../graphs/velocity_vs_distance.png}
  \caption{todo}
  \label{fig:uncorrected_uncalibrated}
\end{figure}

@@

To compute a model, we use non-parametric regression via repeated means as described in
\citet{siegel1982}. A comparison of both models is shown in Figure .

@@
